\documentclass[12pt,letterpaper]{article}

%––––––––––––––––––––––––––––––––––––––––––––––––
% Page geometry
%––––––––––––––––––––––––––––––––––––––––––––––––
\usepackage[
  ignoreheadfoot,
  top=1.5cm,bottom=1.5cm,
  left=2cm,right=2cm,
  footskip=1cm
]{geometry}

%––––––––––––––––––––––––––––––––––––––––––––––––
% Fonts & Unicode
%––––––––––––––––––––––––––––––––––––––––––––––––
\usepackage{iftex}
\ifPDFTeX
  \usepackage{cmap}
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \input{glyphtounicode}
  \pdfgentounicode=1
  \IfFileExists{XCharter.sty}{\usepackage{XCharter}}{\usepackage{charter}}
\else
  \usepackage{fontspec}
  \IfFontExistsTF{XCharter}{\setmainfont{XCharter}}{\setmainfont{Charter}}
\fi
\usepackage{microtype}

%––––––––––––––––––––––––––––––––––––––––––––––––
% Title, lists, icons, links
%––––––––––––––––––––––––––––––––––––––––––––––––
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{accsupp}
\usepackage{xcolor}
\usepackage{hyperref}
\urlstyle{same}
\NewDocumentCommand{\faAlt}{o m}{%
  \BeginAccSupp{ActualText=\IfValueTF{#1}{#1}{#2}}\faIcon{#2}\EndAccSupp{}}

%––––––––––––––––––––––––––––––––––––––––––––––––
% Layout helpers
%––––––––––––––––––––––––––––––––––––––––––––––––
\usepackage{needspace}
\usepackage{changepage}
\usepackage{paracol}

%––––––––––––––––––––––––––––––––––––––––––––––––
% Global formatting
%––––––––––––––––––––––––––––––––––––––––––––––––
\raggedright
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{0.2cm}
\pagenumbering{gobble}
\setcounter{secnumdepth}{0}

% Hyperref metadata and colours
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=cyan,
  pdfauthor={Aleksei Spiridonov},
  pdftitle={CV — Aleksei Spiridonov}
}

\titleformat{\section}
  {\needspace{4\baselineskip}\bfseries\large}
  {}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing*{\section}{0pt}{0.4cm}{0.25cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

%––––––––––––––––––––––––––––––––––––––––––––––––
% Convenience environments
%––––––––––––––––––––––––––––––––––––––––––––––––
\newenvironment{highlights}{%
  \begin{itemize}[topsep=.12cm,parsep=.08cm,itemsep=0pt,leftmargin=10pt]}{%
  \end{itemize}}

\newenvironment{block}{%
  \begin{adjustwidth}{0pt}{0pt}}{%
  \end{adjustwidth}}

% Two-column entry: left column is right-aligned label, right column is normal ragged right
\newenvironment{twocolentry}[1]{%
  \begin{adjustwidth}{0pt}{0pt}%
  \setcolumnwidth{4cm,\fill}%
  \begin{paracol}{2}%
  {\raggedleft #1}\switchcolumn
  \noindent\begin{minipage}[t]{\linewidth}
  \raggedleft
}{%
  \end{minipage}
  \end{paracol}\end{adjustwidth}}

\newcommand{\tripledotsline}{%
  \noindent\makebox[\linewidth]{\hspace{.5em}\dots\hspace{.5em}}}

%––––––––––––––––––––––––––––––––––––––––––––––––
% Document
%––––––––––––––––––––––––––––––––––––––––––––––––
\begin{document}

% ---------- Header ----------
\begin{center}\linespread{1.4}\selectfont%
  {\fontsize{25pt}{25pt}\selectfont Aleksei Spiridonov\par}
  \vspace{6pt}
  \textbf{DevOps Engineer | Kubernetes | Terraform | GitLab CI | Helm}\par
  \vspace{6pt}
  \faAlt[email]{envelope}\;\href{mailto:karasikuk@gmail.com}{karasikuk@gmail.com}\hspace{10pt}%
  \faAlt{whatsapp}\;\href{https://wa.me/995558544273}{+995\,558\,54\,42\,73}\hspace{10pt}%
  \faAlt{telegram}\;\href{https://t.me/baguette_boat}{@baguette\_boat}\par%
  \faAlt{linkedin}\;\href{https://www.linkedin.com/in/aleksei-sp}{www.linkedin.com/in/aleksei-sp}\hspace{10pt}%
  \faAlt{github}\;\href{https://github.com/basenc}{github.com/basenc}\par%
\end{center}

% ---------- Summary ----------
\section{Summary}
\begin{block}
DevOps Engineer with nearly 5 years of experience supporting production Linux systems, CI/CD automation,
Kubernetes workloads, cloud infrastructure, Terraform, Helm, Ansible, and observability stacks.
Experienced in cloud-native operations, release automation, infrastructure as code, GitOps workflows,
production troubleshooting, and reliability-focused engineering.
\end{block}

% ---------- Technical Skills ----------
\section{Technical Skills \& Keywords}
\begin{block}
\textbf{Cloud:} AWS (EKS, EC2, S3, RDS, IAM, VPC), Yandex Cloud\\
\textbf{Containers and Orchestration:} Kubernetes (Ingress, RBAC, HPA, NetworkPolicy), Helm, Werf, Docker\\
\textbf{Infrastructure as Code:} Terraform (modules, remote state, state management, infrastructure-as-code), Ansible\\
\textbf{CI/CD and Release Engineering:} GitLab CI, Azure DevOps\\
\textbf{Observability:} VictoriaMetrics, Prometheus, Grafana (alerting, dashboards), Loki\\
\textbf{Programming and Scripting:} Bash, Python, SQL, JavaScript (NodeJS), YAML\\
\textbf{Systems:} Linux (networking, troubleshooting), Ubuntu, CentOS, Arch Linux, NixOS\\
\textbf{Practices:} GitOps, Infrastructure as Code, DevOps, platform engineering, runbooks,
documentation, cross-functional engineering support
\end{block}

% ---------- Professional Experience ----------
\section{Professional Experience}

\begin{twocolentry}{Aug\,2024 -- Jun\,2026, \textbf{DevOps Engineer}}
  \href{https://mancalagaming.com/}{Mancala Gaming \faLink} (remote)
\end{twocolentry}
\begin{block}
  \begin{highlights}
    \item Executed workload migration between Kubernetes clusters, coordinating namespace setup,
    service endpoint cutover, and traffic shifting for backend microservices.
    \item Migrated container image registry from Nexus to GitLab OCI, consolidating artifact storage
    within the existing CI/CD platform.
    \item Authored Helm charts for backend microservices, covering ingress, HPA, and RBAC configurations
    with templated values for multi-environment deployments.
    \item Maintained and troubleshot GitLab CI/CD pipelines for high-traffic backend microservices.
    \item Improved production observability with VictoriaMetrics, Loki, and OpenTelemetry, surfaced through
    Grafana dashboards and alerts.
    \item Reduced operational risk by documenting runbooks and standardising incident recovery procedures.
  \end{highlights}
\end{block}

\tripledotsline

\begin{twocolentry}{Mar\,2023 -- Aug\,2024, \textbf{DevOps Engineer}}
  \href{https://webtronics.ru/}{Webtronics \faLink} (remote)
\end{twocolentry}
\begin{block}
  \begin{highlights}
    \item Launched TouchWallet mobile crypto wallet backend infrastructure from scratch to production on AWS EKS.
    \item Deployed and maintained blockchain full nodes, ensuring chain synchronisation and data availability.
    \item Managed development and staging Kubernetes environments on AWS EKS, maintaining configuration parity
    with production.
    \item Designed GitLab CI/CD pipelines, reducing release preparation time and improving deployment repeatability.
    \item Managed backend infrastructure with Terraform (including custom modules) and Infrastructure as Code practices.
    \item Onboarded and mentored a junior system administrator.
  \end{highlights}
\end{block}

\tripledotsline

\begin{twocolentry}{Feb\,2022 -- Feb\,2023, \textbf{Tier-2 Linux Technical Support / Junior DevOps}}
  \href{https://web.archive.org/web/20221005062315/https://piratos.cc/}{PiratOS \faLink} (remote)
\end{twocolentry}
\begin{block}
  \begin{highlights}
    \item Administered and monitored Kubernetes workloads for an on-prem Linux-based cryptocurrency
    mining rig platform, improving alert accuracy with Prometheus and Grafana.
    \item Implemented CI/CD release automation with Azure DevOps, Helm, and Ansible.
    \item Resolved Tier-2 Linux, networking, and product issues for on-prem client installations.
  \end{highlights}
\end{block}

\tripledotsline

\begin{twocolentry}{Feb\,2020 -- Jan\,2021, \textbf{Tier-2 Linux Technical Support}}
  \href{https://dc2b.ru/}{Direct Credit \faLink} (Moscow, on-site)
\end{twocolentry}
\begin{block}
  \begin{highlights}
    \item Resolved Linux, network, workstation, and server issues.
  \end{highlights}
\end{block}

% ---------- Education ----------
\section{Education}

\begin{block}
\textbf{National Research University Moscow Power Engineering Institute (MPEI)}\\
Coursework in Radio Engineering

Relevant coursework: Programming, Circuit Theory, Calculus, Classical Field Theory, Radio Technology
\end{block}

% ---------- Certifications ----------
% \section{Certifications}

% \begin{block}
% \end{block}

\end{document}
